---
title: "Tidy Output for Blinder-Oaxaca Decomposition"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The `oaxacad` package is a simple package allowing to output results from a Blinder-Oaxaca decomposition. This package is a wrapper of the `oaxaca` package.

Install the package directly from **github** with

```{r, message=FALSE, error=FALSE, warning=FALSE}
library(devtools)
# install_github("giacomovagni/oaxacad")
```

## Dependencies

To use `microecon` package please make sure you have installed the `tidyverse` and `ggthemes` libraires.

```{r, message=FALSE, error=FALSE, warning=FALSE}
library(oaxaca)
library(tidyverse)
library(broom)
library(gtools)
#
library(oaxacad)
```


# Simulate Data for Decomposition

The function `oaxaca_data` allows a simple way to simulate data for testing the Oaxaca decomposition.

We have two groups (A and B, or 0 and 1). 

Imagine that we want a dataset with a gap only due to observed characteristics (`X`). We set the value for group A with `xA_avr = 10` and the values for group B with `xB_avr = 5`. 

The intercepts between the two groups are the same, `interceptA_avr = 100`, `interceptB_avr = 100`, and the coefficients (the regression' $$\beta$$) are the same `betaA = 5`, `betaB = 5`.


```{r}
output = oaxaca_data(interceptA_avr = 100, interceptB_avr = 100, betaA = 5, betaB = 5, xA_avr = 10, xB_avr = 5)
```

The function output a plot for the two groups

```{r}
output$fig
```

