---
title: "Tidy Output for Blinder-Oaxaca Decomposition"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The `oaxacad` package is a simple package allowing to output results from a Blinder-Oaxaca decomposition. This package is a wrapper of the `oaxaca` package.

Install the package directly from **github** with

```{r, message=FALSE, error=FALSE, warning=FALSE}
library(devtools)
install_github("giacomovagni/oaxacad")
```

## Dependencies

To use `microecon` package please load the following libraries.

```{r, message=FALSE, error=FALSE, warning=FALSE}
library(oaxaca)
library(tidyverse)
library(broom)
library(gtools)
#
library(oaxacad)
```


# Simulate Data for Decomposition

The function `oaxaca_data` allows a simple way to simulate data for testing the Oaxaca decomposition.

We have two groups (A and B, or 0 and 1), and an outcome $Y$.

Imagine that we want a simulated dataset with a *gap* that is only due to **observed characteristics** (`X`). 

The function allows to set one variable for observed characteristics. The variable is normally distributed and the user can set the mean and the sd.

In the function `oaxaca_data`, we can set the mean value of characteristics for group A with `xA_avr = 10` and the mean value for group B with `xB_avr = 5`. 

The intercepts between the two groups are the same, `interceptA_avr = 100`, `interceptB_avr = 100`, and the coefficients (the regression' $\beta$) are the same `betaA = 5`, `betaB = 5`.

```{r}
output = oaxaca_data(interceptA_avr = 100, interceptB_avr = 100, betaA = 5, betaB = 5, xA_avr = 10, xB_avr = 5)
```

The function output a plot for the two groups

```{r}
output$fig
```

The $X$ axis shows the difference in observed characteristics (`X`), and on the $Y$ axis the gap in the outcome `Y`.

The simulated data can be found in `output$dataframe`

------------------------------------------------------------

The function `oaxaca_sim()` takes the same inputs as the function `oaxaca_data` but provides all the computations of the decomposition internally, allowing easy simulations.

```{r, message=FALSE, warning=FALSE}
sim1 = oaxaca_sim(betaA = 5, betaB = 8, xA_avr = 10, xB_avr = 10)
sim2 = oaxaca_sim(betaA = 5, betaB = 5, xA_avr = 8, xB_avr = 10)

sim1$simulated_data$fig
sim2$simulated_data$fig
```

```{r}
sim1$decomp_reg
```

```{r}
sim2$decomp_reg
```


------------------------------------------------------------

## Using the Oaxaca function

We compute the decomposition using the following command

```{r, warning=FALSE, message=FALSE}
#
output = oaxaca_data(interceptA_avr = 100, interceptB_avr = 110, betaA = 10, betaB = 5, xA_avr = 10, xB_avr = 5)
# using the package oaxaca
output = oaxaca::oaxaca(Y ~ X | group, data=output$dataframe)
```

------------

We can tidy several outputs from the oaxaca function

```{r}
Decomp_simple(output)
```

```{r}
Decomp_Regression(output)
```

```{r}
Decomp(output)
```



